\Title

### 2020-03-03 manuscript/manuscript.tex
Add damping to table
Improve how damping values are shown. Instead of showing a full list or
a range, using dots between first two values and last.

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}
\input{parameters_ground_survey.tex}
\input{parameters_airborne_survey.tex}
\input{best_parameters_ground_survey.tex}
\input{best_parameters_airborne_survey.tex}
\input{source_layouts_schematics.tex}

@@

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
            points that resemble a ground survey.
        (b) Location of the \SourceLayoutsSchematicsSourceBellowData{} sources
            obtained through the \emph{sources beneath data} layout.
        (c) Location of the \SourceLayoutsSchematicsBlockMedianSources{}
            sources obtained through the \emph{block averaged sources} layout.
        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
            obtained through the \emph{grid sources} layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \GroundSourceBellowDataConstantDepthDepth
                   & \GroundBlockMedianSourcesConstantDepthDepth
                   & \GroundGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesConstantDepthSpacing
                     & \GroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \GroundGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBellowDataRelativeDepthDepth
                   & \GroundBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBellowDataVariableDepthDepth
                   & \GroundBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \GroundSourceBellowDataVariableDepthKNearest
                  & \GroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}

>>>>

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}
\input{parameters_ground_survey.tex}
\input{parameters_airborne_survey.tex}
\input{best_parameters_ground_survey.tex}
\input{best_parameters_airborne_survey.tex}

@@

\num{1e3}

@@

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c | l l c c}
        \multicolumn{1}{c}{\textbf{Source layout}}
            & \multicolumn{1}{c}{\textbf{Depth type}}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \multicolumn{1}{c}{\textbf{Values}}
            & \multicolumn{1}{c}{\textbf{Interval}} \\
        \hline

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (km)
                & \GroundSourceBellowDataConstantDepthDepth
                & \GroundSourceBellowDataConstantDepthDepthInterval \\
            &
                & Damping
                & \GroundSourceBellowDataConstantDepthDamping
                & \GroundSourceBellowDataConstantDepthDampingInterval \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (km)
                & \GroundSourceBellowDataRelativeDepthDepth
                & \GroundSourceBellowDataRelativeDepthDepthInterval \\
            &
                & Damping
                & \GroundSourceBellowDataRelativeDepthDamping
                & \GroundSourceBellowDataRelativeDepthDampingInterval \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (km)
                & \GroundSourceBellowDataVariableDepthDepth
                & \GroundSourceBellowDataVariableDepthDepthInterval \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                & \GroundSourceBellowDataVariableDepthDepthFactorInterval \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                & \GroundSourceBellowDataVariableDepthKNearestInterval \\
            &
                & Damping
                & \GroundSourceBellowDataVariableDepthDamping
                & \GroundSourceBellowDataVariableDepthDampingInterval \\
        \hline

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesConstantDepthDepth
                & \GroundBlockMedianSourcesConstantDepthDepthInterval \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundBlockMedianSourcesConstantDepthSpacingInterval \\
            &
                & Damping
                & \GroundBlockMedianSourcesConstantDepthDamping
                & \GroundBlockMedianSourcesConstantDepthDampingInterval \\
            \cline{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                & \GroundBlockMedianSourcesRelativeDepthDepthInterval \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \GroundBlockMedianSourcesRelativeDepthSpacingInterval \\
            &
                & Damping
                & \GroundBlockMedianSourcesRelativeDepthDamping
                & \GroundBlockMedianSourcesRelativeDepthDampingInterval \\
            \cline{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesVariableDepthDepth
                & \GroundBlockMedianSourcesVariableDepthDepthInterval \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                & \GroundBlockMedianSourcesVariableDepthDepthFactorInterval \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                & \GroundBlockMedianSourcesVariableDepthKNearestInterval \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \GroundBlockMedianSourcesVariableDepthSpacingInterval \\
            &
                & Damping
                & \GroundBlockMedianSourcesVariableDepthDamping
                & \GroundBlockMedianSourcesVariableDepthDampingInterval \\
        \hline

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (km)
                    & \GroundGridSourcesConstantDepthDepth
                    & \GroundGridSourcesConstantDepthDepthInterval \\
            &
                & Spacing (km)
                    & \GroundGridSourcesConstantDepthSpacing
                    & \GroundGridSourcesConstantDepthSpacingInterval \\
            &
                & Pad
                    & \GroundGridSourcesConstantDepthPad
                    & \GroundGridSourcesConstantDepthPadInterval \\
            &
                & Damping
                    & \GroundGridSourcesConstantDepthDamping
                    & \GroundGridSourcesConstantDepthDampingInterval \\
    \end{tabular}
\end{table*}
